Figures and Tables

### 2021-02-03 paper/figures_tables.Rmd
updates

```{r fig.width=6, fig.height=2.5}
# shape
exptail <- 1
thintail <- 2
fattail <- 0.4

@@

```{r fig.width=6}

@@

@@

plot_grid(histograms_by_id, boxplots, nrow=2, labels = c("A", ""))

@@

@@

## Weibull seed dispersal kernel 
```{r}
knitr::kable(weibull_table)
```

@@

>>>>

```{r fig.width=6, fig.height=2.5}

## 
# Need to change the order of the lines assigned and the legend

##
# shape
exptail <- 1
thintail <- 2
fattail <- 0.4

@@

```{r fig.width=6, fig.height=7}

@@

dispersal_data %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "grey") +
  geom_density(aes(x = dispersal), color = "red") +
  # stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  facet_wrap(~model, ncol = 3) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> dens_by_id

@@

plot_grid(dens_by_id, boxplots, nrow=2, labels = c("A", ""))

@@

```{r eval=FALSE}

dispersal_data %>% 
  filter(., model == "Null") %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  lims(y = c(0, 0.009)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> a

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  lims(y = c(0, 0.009)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> b

dispersal_data %>% 
  filter(., model == "Family") %>% 
  ggplot() +
  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
  lims(y = c(0, 0.009)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> c

plot_grid(a, b, c)

@@

## Weibull seed dispersal kernel

```{r}
knitr::kable(weibull_table)
```

@@

## Figures for seed dispersal kernels and comparison to the fit
Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family. The reason for this, is that when you sample seedlings or seed dispersal distances, you don't know which animal moved which, you just get plant level information and distance to the parent tree. So, now, we visualize the seed dispersal kernels for each of the three models, without considering the variation contributed to the kernel by each individual.

```{r}
# Fit to the data?

dispersal_data %>% 
  ggplot(aes(x = dispersal, linetype = model)) +
  stat_density(geom = "line", position = "identity") +
  # geom_function(aes(color = "Null"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> dispersal_data_plot

dispersal_data_plot +
  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
  #theme_minimal_hgrid(8) +
  theme(legend.position = "none", 
        axis.title = element_blank()) -> dispersal_inset

ggdraw() +
  draw_plot(dispersal_data_plot) +
  draw_plot(dispersal_inset, x = 0.4, y = 0.35, width = 0.5, height = 0.4) -> plot.with.inset

plot.with.inset

# ggsave(filename = "test.png", 
#        plot = plot.with.inset,
#        width = 6, 
#        height = 4,
#        units = "in",
#        dpi = 300)

```{r fig.height=9, fig.width=6}
# Fit to the data?

dispersal_data %>% 
  filter(., model == "Null") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> A

A +
  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
  #theme_minimal_hgrid(8) +
  theme(legend.position = "none", 
        axis.title = element_blank()) -> B

ggdraw() +
  draw_plot(A) +
  draw_plot(B, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> C

########

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AA

AA +
  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
  #theme_minimal_hgrid(8) +
  theme(legend.position = "none", 
        axis.title = element_blank()) -> BB

ggdraw() +
  draw_plot(AA) +
  draw_plot(BB, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> CC

#########

dispersal_data %>% 
  filter(., model == "Individual") %>% 
  ggplot(aes(x = dispersal)) +
  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> AAA

AAA +
  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
  #theme_minimal_hgrid(8) +
  theme(legend.position = "none", 
        axis.title = element_blank()) -> BBB

ggdraw() +
  draw_plot(AAA) +
  draw_plot(BBB, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> CCC

plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO")
